Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-08-21 Ben_Manuscripts/structure_paper/Draft.tex
edits in response to comments

  \subsection{Equilibration}

  We developed equilibration schemes for creating dry and wet configurations.
  Both schemes start with an initial configuration generated according to the
  previous guidelines. For wet systems, we added the desired concentration of
  water to the initial configuration and carried out equilibration in the same
  way as the dry systems. First, we fixed monomer head groups in place using
  position restraints with a force constant of 10$^6$ kJ mol$^{-1}$ nm$^{-2}$. We
  gradually released the position restraints by decreasing the force constants
  over a series of NVT simulations. We allowed the resulting unrestrained
  structure to equilibrate for 5 ns in the NPT ensemble with pressure controlled
  by the berendsen barostat followed by NPT equilibration simulations run for at
  least 400 ns using the Parrinello-Rahman barostat. More equilibration details
  are available in section S-\ref{S-section:equilibration}.

@@

  %MRS8: we should ask Matt see if we can give the github repository
  %for the XRD determination in the paper for reproducibility. I will do that. 
  We generated simulated XRD patterns based on atomic coordinates in order to make
  a direct experimental comparison. We modeled all atomic coordinates as Gaussian
  spheres of electron density corresponding to each atom's electronic radius. A 
  three dimensional Fourier transform (FT) of the array of electron density results in a three dimensional
  structure factor which represents the unit cell in reciprocal space. The
  experimental WAXS measurement was made using a vertically aligned film whose 
  pores were oriented perpendicular to the direction of the incident X-ray beam. 
  %BJC6: Below is the part I'm having a hard time putting into words. 
  Although the pores were vertically aligned, the crystalline domains were still
  misaligned with respect to the xy plane. To account for this, we averaged
  2D slices of the structure factor at all angles about $|\mathbf{q}| = (0, 0, z)$.

  We normalized all diffraction patterns relative to R-alkanes. We believe that the
  alkane-alkane density, averaged over all angles, is the feature most likely to be
  replicated between experiment and simulation, as atomistic alkane parameters are 
  relatively well studied. Other features are dependent on 
  system ordering which is likely to have some dependence on initial configuration. 
  We calculated the average intensity within R-alkanes of the experimental pattern,
  $I_{avg}$ and divided all intensities by this value. In this way, the average intensity
  of R-alkanes was equal to 1. When calculating $I_{avg}$, we excluded intensities 
  within $\pm$ 30\degree~of the meridional axis defined by $q_r=0$, since the simulated
  patterns differ from experiment in those regions in all cases. Specifically, in contrast
  to the experimental WAXS pattern, R-$\pi$, as it appears in the simulated diffraction 
  patterns, intersects with R-alkanes (See Figure~\ref{fig:XRDsim}). We set
  an upper bound on the colorbar by multiplying $I_{avg}$ by a scaling factor, $f$. 
  Intensities that appear in the patterns $\geq$ $f\times I_{avg}$ are colored uniformly. 
  We applied the same scaling method to the simulated patterns. We carefully chose a scaling
  factor of $f=3.1$ in order to visibly display all features in all patterns.

@@

  We 
  %MRS12: sounds too much like structure refinement
  %further refined our structural understanding 
  can better understand the structure of the system by simulating X-ray 
  diffraction patterns produced from equilibrated MD trajectories and comparing them
  to experiment (see section~\ref{method:xrd}). We tested systems built with 5 columns
  per pore in the parallel displaced and sandwiched configurations at 300 K in the 
  ordered and disordered basins,
  %MRS12: added
  as those were the most consistent with the most unambiguous X-ray diffraction patterns, the pore-to-pore spacing and the stacking distance.
We generated simulated patterns using the 
  %MRS12: maybe refer to part of methods where we determined which ones were equilibrated?  Also, maybe say locally equilibrated? Since we know it might be only metastable. 
equilibrated
  portion of each simulation trajectory. There are two important factors to take into
  account when looking at differences between experimental XRD and simulated XRD. First,
  the simulated diffraction patterns have some noise, especially along the $q_z$ axis 
  at $q_r$=0, which is where several of the more interesting features are located. This
  is due to the angle averaging of the 3D structure factor around the $q_z$-axis, meaning
  there are fewer samples as  $q_r$ approaches 0. The amount of samples 
  %MRS12: added
  required to
  to converge along
  the $q_z$ axis is analyzed in Supporting Information section S-\ref{S-section:xrd_noise}. 
  More importantly, our simulations do not appear to be long enough to sample truly 
  independent configurations within their respective metastable basins (see 
  section~\ref{section:slow_dynamics}), meaning we must take care in interpreting the
  results of the XRD. The simulated patterns generated for all systems studied are shown
  and compared to experiment in Figure~\ref{fig:XRDsim}.

  %MRS11: the fact that they are not within their metastable basis DOESN'T just affect the noise it affects everything else.  If we had 100 times longer, it would reduce the noise along the z axis a lot, but the peaks would likely still be too intense, as we would have a lot of data long the z, but still be in the timescales that are too slow to reduce the peak intensity. Did a pass above.

@@

			\begin{subfigure}{\textwidth}
				\centering
			    \includegraphics[width=\linewidth]{rzplot_offset_300K_disorder_jet_nocbar.png}
			\end{subfigure}
	\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{0.1\textwidth}
		\centering
		\includegraphics[width=\linewidth]{colorbar_jet.png}
	\end{subfigure}	
	\caption{Simulated XRD patterns show some qualitative agreement with experiment. Shown is a 
	comparison of the (a) Sandwiched, ordered basin (b) Sandwiched,
	disordered basin (d) Parallel displaced, ordered basin and (e) Parallel displaced, disordered basin 
	configurations with (c) experimental WAXS. 	In all cases, R-pores, R-alkanes and R-$\pi$ are 
	present to some degree. R-spots is also present, however it is generally partially covered by the
	broad R-$\pi$ reflection. Quantitative comparisons of the relative intensities of reflections of
	interest are presented in Table~\ref{table:relative_intensities_300K}. In both XRD patterns generated
	from parallel displaced patterns, there is a faint line across $q_z \sim 0.7~$\AA$^{-1}$, half
	the simulated value of R-$\pi$. Although it does not cross through $q_r = 0$~\AA$^{-1}$, it is at 
	the same $q_z$ value where we expect R-double to be present. Still, R-double is not fully reproduced
	in any of the simulated patterns.}~\label{fig:XRDsim} 
        %MRS12: I would repeat the labels from figure 3.  Minimum, need to refer back to that figure so they know where to find the definitions of the lables. 
  \end{figure}

  The simulated XRD patterns show moderate agreement with experiment. There 
  are key qualitative and quantitative differences between the experimental and simulated
  locations and intensities of each major reflection. The integrated intensity and location
  of each simulated reflection relative to its experimental counterpart are shown in  
  Table~\ref{table:relative_intensities_300K}. Our approach for measuring the intensity of
  each reflection are described in section S-\ref{S-section:xrd_intensities}. %MRS12: should that be in Methods instead of suporting?  Not sure.

@@

  \begin{table}[h]
  \centering
  \begin{tabular}{c|ccccc}
  \toprule
 		     & \multicolumn{5}{c}{Normalized Reflection Intensity}                   \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes  & 1.0        &  1.0       &  1.0      &  1.0       &  1.0               \\
  R-pores    & 12.3       & 49.5       & 54.0      & 50.8       & 53.4               \\
  R-spots    & 1.2        &  1.2       &  1.2      &  1.1       &  1.1               \\
  R-$\pi$    & 2.8        & 44.0       &  7.7      &  8.4       & 10.1               \\
  R-double   & 0.9        &  --        & --        &  --        & --                 \\ 
  \hline
   		     & \multicolumn{5}{c}{Reflection Location ($|\mathbf{q}|~\AA^{-1}$)}     \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes  & 1.39       &  1.44      &  1.44     & 1.42       & 1.43               \\  
  R-pores    & 0.176      &  0.170     &  0.170    & 0.173      & 0.172              \\
  R-spots    & 1.39       &  1.44      &  1.44     & 1.42       & 1.43               \\
  R-$\pi$    & 1.70       &  1.41      &  1.42     & 1.40       & 1.40               \\
  R-double   & 0.85       &  --        & --        &  --        & --                 \\ 
  \bottomrule
  \end{tabular}
  %MRS12: question: is the normalization for the simulated systems the same, no matter if disordered, etc.  If not chosen to be exactly the same, how different are they? 
  \caption{The simulated XRD patterns of the systems tested, normalized so that the average 
  intensity of R-alkanes in each pattern equals 1, show R-$\pi$ reflections that are significantly higher 
  than experiment and R-spots reflections that are slightly lower than experiment. R-double
  does not appear in any simulated patterns, and thus has no measurable intensity.}
  \label{table:relative_intensities_300K} 
  \end{table}

@@

  We normalized the experimental and simulated diffraction patterns so that the average
  intensity within R-alkanes is equal to 1 because we believe that R-alkanes is the
  experimental feature most likely to be reproduced by our simulations. 
  %BJC11: could add some support of this statement - perhaps a reference to the original
  % GAFF forcefield paper? Need to actually check it though.
  %MRS12: first pass.  
  We reach this conclusion because alkane
  parameters in GAFF and AMBER forcefields are generally reproduce data well.~\cite{original_gaff_paper} 
  %MRS12: Citation is: https://doi.org/10.1002/jcc.20035  could also cite: https://pubs.acs.org/doi/pdf/10.1021/ct200731v
  %MRS12: below - say what appears close means?  radius of max is X vs Y.
  R-alkanes appears close to its expected location. In all cases, the maximum intensity
  of R-alkanes appears at a $|\mathbf{q}|$ value only slightly higher than experiment. 
  %MRS12: different pass? Though need to specify WHAT the error is.  Can't be intensity, since that is what we are normalizing by, so is it LOCATION of the intensity?  Also, need to verify the statement is correct.  Could still good languange if the conclusion was that the binning error was similar in size to errors in the location R-alkane.
  The error in the simulated diffraction patterns is less that the error due binning in eack frequency direction, so was not further investigated. 
  %We expect that the exact location of R-alkanes will not be perfect in our simulations
  %since the simulated diffraction patterns are interpolated between a finite number of
  %bins in each frequency dimension. 
  %We can achieve higher resolution with a larger
  %system size, however we are satisfied with the packing distances shown by our simulations.
  %BJC11: I could integrate a 3D correlation function to get a better value.
  %MRS12: saying ``we are satisfied'' opens to claims that reviwers say ``well, I'm not''.  Pass at this above.

@@

  R-pores is about 4 times more intense than experiment in all simulated systems. We
  hypothesize that this is primarily due to the relatively perfect infinite hexagonal
  array of pores in the simulated systems. In the real system, periodicity of the 
  hexagonal array is disrupted by misalignment of the crystalline domains and the
  pore-to-pore distances fluctuate more over long time scales. 
  % BJC11: Using simple systems, I can show that more highly fluctutating pore-to-pore
  % distances will decrease the intensity of R-pores. I don't think its worth getting
  % into in the main text. It's the same idea as how increased z-noise decreases the intensity of R-pi
  % BJC11: I also think that domain misalignment in the z-direction contributes. If you
  % imagine a hexagonal array of pores aligned along the z-axis, then rotate that axis
  % so it has an x and y component, then there will be constructive interference perpendicular
  % to that axis at non-zero qz values. That is why R-pores is arced. It's a different
  % type of broadening than R-pi - I think
  % BJC11: I don't think a deep dive into this is worth it. It's dependent on things
  % unrelated to the actual pore structure.
  % MRS12:  Agreed. Rephrased a bit.
  The agreement in intensity in R-pores obtained here is sufficient for this study because this intensity is primarily controlled by longer-range organization that cannot be captured by simulation of only 4 pores and because we are concered with the with the structure of the individual pores themselves.

  The location of the leading peak of R-pores is directly related to the average 
  distance between pores. However, there is substatial uncertainty in the exact location 
  relative to the bin size used for the Fourier space transformation. We can instead 
  measure the average distance between columns
  with more precision in real space (See Section~\ref{method:pore_spacing}). We showed
  that we achieve experimentally consistent pore spacings in our simulations in 
  Section~\ref{section:section:mon_per_pore}.

@@

  The intensity of R-spots is close to experiment when generated from any of our
  simulated systems. 
  Because the R-spots reflection is difficult to distinguish visually as it appears 
  at the same $|\mathbf{q}|$ as R-alkanes, we calculate 
  the intensity of R-spots by assuming that its $q_z$ location should be roughly in line with 
  the experimental R-double, half the $q_z$ distance of R-$\pi$).
  %The appearance of R-spots is inconspicuous in most cases so we
  %assumed that the location of R-spots, in terms of $|\mathbf{q}|$ would coincide with
  %that of R-alkanes, and that it's $q_z$ location should be roughly in line with 
  %R-double (half the $q_z$ location of R-$\pi$) as it appears in the experimental pattern.
  We measured the intensity of R-spots by radially integrating the simulated
  diffraction pattern between $1.4~\AA^{-1} < |\mathbf{q}| < 1.57~\AA^{-1}$ (between
  4 and 4.5 $\AA$ in real space) and then locating and recording the intensity of the 
  appropriate peaks in the resulting distribution.

  %MRS12: here I'm going to break the rule of the thesis statement, since it reads strangely to have thesis, contradition, repeat thesis, there isn't any evidence. But it flows OK this way.   
  %R-spots is most likely a result of ordered packing of the monomer's alkyl tails. 
  Previous literature has attributed the R-spots reflection in this particular WAXS dataset as 
  the result of tilted alkane chains~\cite{feng_scalable_2014}. 
  %Here we refute that explanation and show that the 
  We measured the tilt angle of the alkane chains of
  the 280K system and found that it equilibrates to an average tilt angle of
  -2\degree~(Fig.~\ref{fig:tilt}), far from the 37\degree~tilt angle previously
  used to explain R-spots. Similar lack of more than a statistically negligible tilt occured when 
  we performed the simulations with a number of other starting configurations, obtaining similar results.%MRS12: I know we discussed this earlier; there were a number of things that were done to verify this results was consistent, and I think that a rief summary would help.

@@

  The Evidence from the simulations strongly suggests that the R-spots signal
 is not a 
  result of alkane chain tilt.

@@

  The position, shape and intensity of R-$\pi$, generated from simulations at 300K, are 
  qualitatively similar to experiment, but have significant quantitative differences. The reflections appear
  at lower $q_z$ values, they are more intense, and the shape of its cross-sections, 
  especially in the $q_r$ direction are different relative to the experimental system.
  For comparison, see Figure~\ref{fig:rpi_exp_comparison} where we used cross-sections of the simulated
  XRD generated from the ordered parallel displaced configuration as an example. In 
  this section, we explore the various contributions to these discrepancies, and use this information to 
  speculate on what reasonable differences in the simulations could explain the discrepancies.

@@

  An exact quantitative comparison between the intensity and FWHM of the experimental
  and simulated cross-sections of R-$\pi$ is not feasible
  for several reasons. Experimental peaks broaden due to effects that we can not 
  easily simulate such as finite size crystalline domains and instrumental resolution.
  In our simulated XRD patterns, the system size imposes limitations on the resolution,
  which makes it difficult to reliably fit peaks. This is especially problematic when
  comparing the FWHM of the $q_z$ cross-section of R-$\pi$, where the experimental 
  FWHM (0.11 $\AA^{-1}$) is similar to the bin size in the $q_z$ direction (ca. 0.07 $\AA^{-1}$).
  Additionally, we model each atom with a Gaussian sphere of electron density, which is a simplification. 
  However, we can explore reasons for which differences in the simulation structure could change
  the peak shapes and intensities to be in better agreement with experiment.

>>>>

  \subsection{Equilibration}\label{section:equilibration}
  We developed equilibration schemes for creating dry and wet configurations.
  Both schemes start with an initial configuration generated according to the
  previous guidelines. For wet systems, we added the desired concentration of
  water to the initial configuration and carried out equilibration in the same
  way as the dry systems. First, we fixed monomer head groups in place using
  position restraints with a force constant of 10$^6$ kJ mol$^{-1}$ nm$^{-2}$. We
  gradually released the position restraints by decreasing the force constants
  over a series of NVT simulations. We allowed the resulting unrestrained
  structure to equilibrate for 5 ns in the NPT ensemble with pressure controlled
  by the berendsen barostat followed by NPT equilibration simulations run for at
  least 400 ns using the Parrinello-Rahman barostat. More equilibration details
  are available in section S-\ref{S-section:equilibration}.

@@

  We generated simulated XRD patterns based on atomic coordinates in order to make
  a direct experimental comparison. We modeled all atomic coordinates as Gaussian
  spheres of electron density corresponding to each atom's electronic radius. A 
  three dimensional Fourier transform (FT) of the array of electron density results in a three dimensional
  structure factor which represents the unit cell in reciprocal space. The
  experimental WAXS measurement was made using a vertically aligned film whose 
  pores were oriented perpendicular to the direction of the incident X-ray beam. 
  %BJC6: Below is the part I'm having a hard time putting into words. 
  Although the pores were vertically aligned, the crystalline domains were still
  misaligned with respect to the xy plane. To account for this, we averaged
  2D slices of the structure factor at all angles about $|\mathbf{q}| = (0, 0, z)$.

  We normalized all diffraction patterns relative to R-alkanes. We believe that
  the alkane-alkane density, averaged over all angles, is the feature most likely
  to be replicated between experiment and simulation, as atomistic alkane
  parameters are relatively well studied. Other features are dependent on system
  ordering which is likely to have some dependence on initial configuration.  We
  calculated the average intensity within R-alkanes of the experimental pattern,
  $I_{avg}$ and divided all intensities by this value. In this way, the average
  intensity of R-alkanes was equal to 1. When calculating $I_{avg}$, we excluded
  intensities within $\pm$ 30\degree~of the meridional axis defined by $q_r=0$,
  since the simulated patterns differ from experiment in those regions in all
  cases (See Figure~\ref{fig:ralkanes}). Specifically, in contrast to the
  experimental WAXS pattern, R-$\pi$, as it appears in the simulated diffraction
  patterns, intersects with R-alkanes (See Figure~\ref{fig:XRDsim}). We set an
  upper bound on the colorbar by multiplying $I_{avg}$ by a scaling factor, $f$.
  Intensities that appear in the patterns $\geq$ $f\times I_{avg}$ are colored
  uniformly.  We applied the same scaling method to the simulated patterns. We
  carefully chose a scaling factor of $f=3.1$ in order to visibly display all
  features in all patterns.

%BJC12: redundant -- copied from methods
%  We developed standardized methods of measuring the intensity of reflections of interest
%  in the experimental and simulated X-ray diffraction patterns presented in this work. Here,
%  we graphically illustrate the methods used for measuring these intensities.

%  All diffraction patterns are normalized according to R-alkanes and the intensities
%  of all reflections are reported relative to the intensity of R-alkanes. The region
%  used to calculate the average intensity of R-alkanes is shown in
%  Figure~\ref{fig:ralkanes}. The top region is excluded because, in the simulated
%  patterns, R-$\pi$ intersects with R-alkanes.

  We reported the intensities of R-$\pi$ and R-double by recording the maximum values
  of the peaks of the $q_z$ cross-section of the experimental pattern at $q_r=0$ 
  (Figure~\ref{fig:rpi_rdouble}). In the case of the experimental pattern, the peak
  heights are not perfectly symmetrical, so we report the average of the two heights.

  We measured the intensity of R-spots by averaging the peak heights produced
  by radially integrating the patterns within the R-alkanes region
  (Figure~\ref{fig:rspots}).  In some patterns, the spots are not easily
  discernable due to obstruction by other features. In that case, we report the
  average intensity at the intersection of R-alkanes with the $q_z$ value of
  R-double since that is where we expect it to appear based on experiment. Since
  R-double does not appear in our simulated patterns, we estimate where it should
  appear as half of the $q_z$ value of R-$\pi$.

 % We measured the intensity of R-spots by calculating the average intensity
 % within a region selected by visual inspection. We report the average intensity
 % within the regions highlighted in red in Figure~\ref{fig:rspots}.

  We measured the intensity of R-pores based on the intensity of the leading peak
  (closest to $q_r$ = 0) of the $q_r$ cross-section of the patterns at $q_z$=0
  (Figure~\ref{fig:saxs_xsection}). The beamstop covers most of the small angle
  reflections in the experimental 2D WAXS pattern. In order to compare the simulated
  intensity of R-pores to experiment, we used the $q_r$ cross-section of 2D SAXS 
  which was generated from the same sample. Since the d\textsubscript{110} peak is  %BJC12: verify which crystal plane it is.
  partially exposed in the experimental 2D WAXS pattern, we normalized the experimental 
  2D SAXS cross-section by matching the intensity of the d\textsubscript{110} peak 
  between it and the experimental 2D WAXS cross-section. It is possible that the peak
  is not fully captured in the 2D WAXS pattern and that our estimate of the intensity
  of R-pores for the experimental pattern is underestimated.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\linewidth}
  \centering
  \includegraphics[width=\textwidth]{ralkanes.png}
  \caption{R-alkanes}\label{fig:ralkanes}
  \end{subfigure}
  \begin{subfigure}{0.45\linewidth}
  \centering
  \includegraphics[width=\textwidth]{rpi_rdouble.png}
  \caption{$q_z|_{r=0}$}\label{fig:rpi_rdouble}
  \end{subfigure}
  \begin{subfigure}{0.45\linewidth}
  \centering
  \includegraphics[width=\textwidth]{angular_integration.png}
  \caption{R-spots}\label{fig:rspots}
  \end{subfigure}
  \begin{subfigure}{0.45\linewidth}
  \centering
  \includegraphics[width=\textwidth]{saxs_xsection.png}
  \caption{R-spots}\label{fig:saxs_xsection}
  \end{subfigure}
  \caption{(a) We measured the intensity of R-alkanes by calculating the average 
  intensity within the region bounded by $|\mathbf{q}|$ = 1.4$\AA^{-1}$ and 
  1.57$\AA^{-1}$ (between 4.0 and 4.5 \AA in real space). We excluded intensities
  within $\pm$ 30\degree~of the meridional axis defined by $q_r=0$, since the 
  simulated patterns differ from experiment in those regions in all cases. (b) We
  measured the intensity of R-$\pi$ and R-double based on the peaks of the $q_z$
  cross-section of the diffraction pattern. (c) We measured the intensity of R-spots
  by averaging the peak heights produced by radially integrating the patterns within 
  the R-alkanes region. We took the intensity of R-spots as the average of the 
  peak intensities near 37 and 143 $\degree$. (d) We measured the intensity of 
  R-pores by measuring the height of the leading peak (closest to $q_r$=0) of 
  the cross-section of the diffraction patterns along the $q_r$ axis at $q_z$=0.} \label{fig:xrd_intensities}
  \end{figure}

@@

  We can better understand the structure of the system by simulating X-ray
  diffraction patterns produced from equilibrated MD trajectories and comparing
  them to experiment (see section~\ref{method:xrd}). We tested systems built with
  5 columns per pore in the parallel displaced and sandwiched configurations at
  300 K in the ordered and disordered basins, as those were the most consistent
  with the most unambiguous X-ray diffraction features, the pore-to-pore spacing
  and the stacking distance.  We generated simulated patterns using the locally
  equilibrated portion of each simulation trajectory (See
  Section~\ref{method:equil_time}. There are two important factors to take into
  account when looking at differences between experimental XRD and simulated XRD.
  First, the simulated diffraction patterns have some noise, especially along the
  $q_z$ axis at $q_r$=0, which is where several of the more interesting features
  are located. This is due to the angle averaging of the 3D structure factor
  around the $q_z$-axis, meaning there are fewer samples as  $q_r$ approaches 0.
  The amount of samples required to to converge along the $q_z$ axis is analyzed
  in Supporting Information section S-\ref{S-section:xrd_noise}.  More
  importantly, our simulations do not appear to be long enough to sample truly
  independent configurations within their respective metastable basins (see
  section~\ref{section:slow_dynamics}), meaning we must take care in interpreting
  the results of the XRD. The simulated patterns generated for all systems
  studied are shown and compared to experiment in Figure~\ref{fig:XRDsim}.

@@

			\begin{subfigure}{\textwidth}
				\centering
			    \includegraphics[width=\linewidth]{rzplot_offset_300K_disorder_jet_nocbar.png}
			\end{subfigure}
	\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{0.1\textwidth}
		\centering
		\includegraphics[width=\linewidth]{colorbar_jet.png}
	\end{subfigure}	
	\caption{Simulated XRD patterns show some qualitative agreement with
		experiment. Shown is a comparison of the (a) Sandwiched, ordered basin (b)
		Sandwiched, disordered basin (d) Parallel displaced, ordered basin and (e)
		Parallel displaced, disordered basin configurations with (c) experimental WAXS.
		The major reflections of interest (See Figure~\ref{fig:SWAXS} for their
		definitions) are present at varying degrees. In all cases, R-pores, R-alkanes
		and R-$\pi$ are present to some degree. R-spots is also present, however it is
		generally partially covered by the broad R-$\pi$ reflection. Quantitative
		comparisons of the relative intensities and locations of reflections of
		interest are presented in Table~\ref{table:relative_intensities_300K}. In both
		XRD patterns generated from parallel displaced patterns, there is a faint line
		across $q_z \sim 0.7~$\AA$^{-1}$, half the simulated value of R-$\pi$. Although
		it does not cross through $q_r = 0$~\AA$^{-1}$, it is at the same $q_z$ value
		where we expect R-double to be present. Still, R-double is not fully reproduced
		in any of the simulated patterns.}~\label{fig:XRDsim} 
  \end{figure}

  The simulated XRD patterns show moderate agreement with experiment. There 
  are key qualitative and quantitative differences between the experimental and simulated
  locations and intensities of each major reflection. The integrated intensity and location
  of each simulated reflection relative to its experimental counterpart are shown in  
  Table~\ref{table:relative_intensities_300K}. Our approach for measuring the intensity of
  each reflection are described in section S-\ref{S-section:xrd_intensities}. 
  %MRS12: should that be in Methods instead of suporting?  Not sure.
  %BJC12: moved into methods for now.

@@

  \begin{table}[h]
  \centering
  \begin{tabular}{c|ccccc}
  \toprule
 		     & \multicolumn{5}{c}{Normalized Reflection Intensity}                   \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes  & 1.0        &  1.0       &  1.0      &  1.0       &  1.0               \\
  R-pores    & 12.3       & 49.5       & 54.0      & 50.8       & 53.4               \\
  R-spots    & 1.2        &  1.2       &  1.2      &  1.1       &  1.1               \\
  R-$\pi$    & 2.8        & 44.0       &  7.7      &  8.4       & 10.1               \\
  R-double   & 0.9        &  --        & --        &  --        & --                 \\ 
  \hline
   		     & \multicolumn{5}{c}{Reflection Location ($|\mathbf{q}|~\AA^{-1}$)}     \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes  & 1.39       &  1.44      &  1.44     & 1.42       & 1.43               \\  
  R-pores    & 0.176      &  0.170     &  0.170    & 0.173      & 0.172              \\
  R-spots    & 1.39       &  1.44      &  1.44     & 1.42       & 1.43               \\
  R-$\pi$    & 1.70       &  1.41      &  1.42     & 1.40       & 1.40               \\
  R-double   & 0.85       &  --        & --        &  --        & --                 \\ 
  \bottomrule
  \end{tabular}
  %MRS12: question: is the normalization for the simulated systems the same, no matter if disordered, etc.  If not chosen to be exactly the same, how different are they?
  %BJC12: Are you asking what the normalization constant is that I divide the patterns by for each system? I'll have to check. 
  \caption{The simulated XRD patterns of the systems tested, normalized so that
	  the average intensity of R-alkanes in each pattern equals 1, show R-pores and
	  R-$\pi$ reflections that are significantly higher than experiment and R-spots
	  reflections that are slightly lower than experiment. R-double does not appear
	  in any simulated patterns, and thus has no measurable intensity.}
  \label{table:relative_intensities_300K} 
  \end{table}

@@

  We normalized the experimental and simulated diffraction patterns so that the
  average intensity within R-alkanes is equal to 1 because we believe that
  R-alkanes is the experimental feature most likely to be reproduced by our
  simulations.  We reach this conclusion because alkane parameters in GAFF and
  AMBER forcefields generally reproduce data well.~\cite{original_gaff_paper} 
  %MRS12: Citation is: https://doi.org/10.1002/jcc.20035  could also cite: https://pubs.acs.org/doi/pdf/10.1021/ct200731v

  %MRS12: below - say what appears close means?  radius of max is X vs Y.
  R-alkanes appears close to its expected location. In all cases, the maximum
  intensity of R-alkanes along the $q_r$ axis at $q_z$=0, which we use to
  estimate its location, appears at a $|\mathbf{q}|$ value that is, at most,
  3.5\% higher than higher than experiment. 
  %MRS12: different pass? Though need to specify WHAT the error is.  Can't be intensity, since that is what we are normalizing by, so is it LOCATION of the intensity?  Also, need to verify the statement is correct.  Could still good languange if the conclusion was that the binning error was similar in size to errors in the location R-alkane.
  %BJC12: I use the maximum intensity of R-alkanes along the q_r axis at qz=0 to determine its location.
  The error in the simulated diffraction patterns is less that the error due
  binning in each frequency direction, so was not further investigated. 
  %We expect that the exact location of R-alkanes will not be perfect in our simulations
  %since the simulated diffraction patterns are interpolated between a finite number of
  %bins in each frequency dimension. 
  %We can achieve higher resolution with a larger
  %system size, however we are satisfied with the packing distances shown by our simulations.
  %BJC11: I could integrate a 3D correlation function to get a better value.
  %MRS12: saying ``we are satisfied'' opens to claims that reviwers say ``well, I'm not''.  Pass at this above.

@@

  R-pores is about 4 times more intense than experiment in all simulated
  systems. We hypothesize that this is primarily due to the relatively perfect
  infinite hexagonal array of pores in the simulated systems. In the real system,
  periodicity of the hexagonal array is disrupted by misalignment of the
  crystalline domains and the pore-to-pore distances fluctuate more over long
  time scales. 
  % BJC11: Using simple systems, I can show that more highly fluctutating pore-to-pore
  % distances will decrease the intensity of R-pores. I don't think its worth getting
  % into in the main text. It's the same idea as how increased z-noise decreases the intensity of R-pi
  % BJC11: I also think that domain misalignment in the z-direction contributes. If you
  % imagine a hexagonal array of pores aligned along the z-axis, then rotate that axis
  % so it has an x and y component, then there will be constructive interference perpendicular
  % to that axis at non-zero qz values. That is why R-pores is arced. It's a different
  % type of broadening than R-pi - I think
  % BJC11: I don't think a deep dive into this is worth it. It's dependent on things
  % unrelated to the actual pore structure.
  % MRS12:  Agreed. Rephrased a bit.
  The agreement in intensity in R-pores obtained here is sufficient for this
  study because this intensity is primarily controlled by longer-range
  organization that cannot be captured by simulation of only 4 pores and because
  we are only concerned with the structure of the individual pores themselves.

  The location of the leading peak of R-pores is directly related to the
  average distance between pores. However, there is substantial uncertainty in
  the exact location relative to the bin size used for the Fourier space
  transformation. We can instead measure the average distance between columns
  with more precision in real space (See Section~\ref{method:pore_spacing}). We
  showed that we achieve experimentally consistent pore spacings in our
  simulations in Section~\ref{section:section:mon_per_pore}.

@@

  The intensity of R-spots is close to experiment when generated from any of
  our simulated systems. We measured the intensity of R-spots by radially integrating the simulated
  diffraction pattern between $1.4~\AA^{-1} < |\mathbf{q}| < 1.57~\AA^{-1}$
  (between 4 and 4.5 $\AA$ in real space) and then locating and recording the
  intensity of the appropriate peaks in the resulting distribution. Because the
  R-spots reflection is difficult to distinguish visually as it appears at the
  same $|\mathbf{q}|$ as R-alkanes, we calculate the intensity of R-spots by
  assuming that its $q_z$ location should be roughly in line with the
  experimental R-double, half the $q_z$ distance of R-$\pi$).

  %MRS12: here I'm going to break the rule of the thesis statement, since it reads strangely to have thesis, contradition, repeat thesis, there isn't any evidence. But it flows OK this way.   
  %R-spots is most likely a result of ordered packing of the monomer's alkyl tails. 
  Previous literature has attributed the R-spots reflection in this particular
  WAXS dataset as the result of tilted alkane chains~\cite{feng_scalable_2014}.
  We measured the tilt angle of the alkane chains of the 280K system and found
  that it equilibrates to an average tilt angle of
  -2\degree~(Fig.~\ref{fig:tilt}), far from the 37\degree~tilt angle previously
  used to explain R-spots. Even when we placed position restraints on the
  monomers in a tilted initial configuration, monomers quickly reduced their tilt
  relative to the $xy$ plane to an angle statisically neglibible from zero. (See 
  Section S-TBD). 
  %Similar lack of more than a statistically negligible
  %tilt occured when we performed the simulations with a number of other starting
  %configurations, obtaining similar results. 
  %MRS12: I know we discussed this earlier; there were a number of things that were done to verify this results was consistent, and I think that a rief summary would help. 
  %BJC12: It was primarily us trying to induce tilt by equilibrating with position restraints. I'm trying to think of what else we might have done. I changed the last sentence for now

@@

%  The Evidence from the simulations strongly suggests that the R-spots signal
% is not a 
%  result of alkane chain tilt.

@@

  The position, shape and intensity of R-$\pi$, generated from simulations at
%  300K, are qualitatively similar to experiment, but have significant
%  quantitative differences. 
% BJC12: I don't think I agree that they are qualitatively similar either. The
% simulated qr cross-sections are spikey and too low (which is qualitatively
% evident when you look at the simulated XRD patterns)
  300K have qualitative and quantitative differences from experiment.
  The reflections appear at lower $q_z$ values, they
  are more intense, and the shape of its cross-sections, especially in the $q_r$
  direction are different relative to the experimental system.  For comparison,
  see Figure~\ref{fig:rpi_exp_comparison} where we used cross-sections of the
  simulated XRD generated from the ordered parallel displaced configuration as an
  example. In this section, we explore the various contributions to these
  discrepancies, and use this information to speculate on what reasonable
  differences in the simulations could explain the discrepancies.

@@

  An exact quantitative comparison between the intensity and FWHM of the
  experimental and simulated cross-sections of R-$\pi$ is not feasible for
  several reasons. Experimental peaks broaden due to effects that we can not
  easily simulate such as finite size crystalline domains and instrumental % reference needed
  resolution.  In our simulated XRD patterns, the system size imposes limitations
  on the resolution, which makes it difficult to reliably fit peaks. This is
  especially problematic when comparing the FWHM of the $q_z$ cross-section of
  R-$\pi$, where the experimental FWHM (0.11 $\AA^{-1}$) is similar to the bin
  size in the $q_z$ direction (ca. 0.07 $\AA^{-1}$).  Additionally, we model each
  atom with a Gaussian sphere of electron density, which is a simplification.
  However, we can explore reasons for which differences in the simulation
  structure could change the peak shapes and intensities to be in better
  agreement with experiment.
